Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-25 paper/ijcai/paper.tex
polishing

\begin{abstract}
Several approaches have been proposed to reduce debugging costs through
automated software fault diagnosis.  Dynamic Slicing (\ds{}) and Spectrum-based
Fault Localization (\sfl{}) are popular fault diagnosis techniques and normally
seen as complementary. This paper reports on a comprehensive
study\comments{--using \numFaults{} documented software faults from a credible
dataset--} to reassess the effects of combining \ds{} with \sfl{}.  With this
combination, components that are often involved in failing but seldom in passing
test runs could be located and their suspiciousness reduced. Results show that
the \ds{}-\sfl{} combination, coined as Tandem-SL, improves the diagnostic
accuracy up to $73.7\%$ (\avgImprov\ on average). Furthermore, results indicate
that the risk of missing faulty statements, which is a \ds{}'s key limitation,
is not high~---~\ds{} misses faulty statements in $9\%$\comments{($23$ misses)}
of the $\numFaults{}$ cases. To sum, we found that the \ds{}-\sfl{} combination
was practical and effective and encourage new \sfl{} techniques to be evaluated
against that optimization.
\end{abstract}

>>>>

\begin{abstract}
Several approaches have been proposed to reduce debugging costs through
automated software fault diagnosis.  Dynamic Slicing (\ds{}) and Spectrum-based
Fault Localization (\sfl{}) are popular fault diagnosis techniques and normally
seen as complementary. This paper reports on a comprehensive
study\comments{--using \numFaults{} documented software faults from a credible
dataset--} to reassess the effects of combining \ds{} with \sfl{}.  With this
combination, components that are often involved in failing but seldom in passing
test runs could be located and their suspiciousness reduced. Results show that
the \ds{}-\sfl{} combination, coined as \comb, improves the diagnostic
accuracy up to $73.7\%$ (\avgImprov\ on average). Furthermore, results indicate
that the risk of missing faulty statements, which is a \ds{}'s key limitation,
is not high~---~\ds{} misses faulty statements in $9\%$\comments{($23$ misses)}
of the $\numFaults{}$ cases. To sum up, we found that the \ds{}-\sfl{} combination
was practical and effective and encourage new \sfl{} techniques to be evaluated
against that optimization.
\end{abstract}
